The Concurrent Calculi Formalisation Benchmark

### 2024-01-30 short-paper/short-paper.tex
Remove outline section of the short paper.
Remove table of extensions from short paper.

\paragraph{Outline of this paper.}
We discuss our design choices in \Cref{sec:design-discussion}, and possible extensions and further topics in \Cref{sec:going-beyond}.
The challenges themselves may be found in \Cref{app:challenges}.

@@

\vspace{-1mm}%
\paragraph{Extending and combining the current challenges.}
While the proposed challenges try to minimise the overlap of the techniques
and aspects they explore (linearity, scope extrusion, coinduction), most
research on concurrency theory combines some or all of these. A second round of formalisations might
entail combining the features of the challenges.
In \Cref{tab:extensions} we consider the following three extensions:
\emph{(1)} the addition of choice to the type level and the process level,
\emph{(2)} the addition of recursion and (for typed systems) recursive types,
and \emph{(3)} the
addition of channel delegation to those calculi that do not already
support it.%
%
\luca{I would argue that support for recursive types and processes may also
impact the coinduction challenge. Indeed, some type systems with support for
recursion are more easily expressed \emph{coinductively}, by allowing possibly
infinite typing derivation. This application of coinduction is different from
that intended in the challenge, where it's focused on expressing notions of
process equivalence, and yet it is increasingly popular (see the related work on
infinitary linear logics) and occasionally seen with skepticism, which would
make a good case for formalization.}\luca{as a follow up to the previous
comment, if there is agreement that recursive types impact the coinduction
challenge then the relevance of Table 1 may be questionable because almost every
extension impacts almost every challenge. In case of need we may consider
removing the table in favor of more prose.}

\begin{table}[btp]
  \caption{Possible extensions of the challenges. Each suitable extension is marked ``+''. \label{tab:extensions} \\}
  \begin{center}\small
    \vspace{-4mm}%
    \begin{tabular}{|r|c|c|c|}
      \hline
      & Linearity & Scope extrusion & Coinduction \\
      \hline
      Choice & $+$ & $+$  & $+$ \\
      \hline
      Recursive types & $+$  & $+$ & \\
      \hline
      Delegation & $+$ & & $+$ \\
      \hline
    \end{tabular}
    \vspace{-3mm}%
  \end{center}
\end{table}

>>>>

@@

\vspace{-1mm}%
\paragraph{Extending and combining the current challenges.}
While the proposed challenges try to minimise the overlap of the techniques
and aspects they explore (linearity, scope extrusion, coinduction), most
research on concurrency theory combines some or all of these. A second round of formalisations might
entail combining the features of the challenges.
We consider the following three extensions:
\emph{(1)} the addition of choice to the type level and the process level,
\emph{(2)} the addition of recursion and (for typed systems) recursive types,
and \emph{(3)} the
addition of channel delegation to those calculi that do not already
support it.%
%
\luca{I would argue that support for recursive types and processes may also
impact the coinduction challenge. Indeed, some type systems with support for
recursion are more easily expressed \emph{coinductively}, by allowing possibly
infinite typing derivation. This application of coinduction is different from
that intended in the challenge, where it's focused on expressing notions of
process equivalence, and yet it is increasingly popular (see the related work on
infinitary linear logics) and occasionally seen with skepticism, which would
make a good case for formalization.}
